### 2020-10-07 2020/WCGO_MCO_OptimizationLetters/2020_WCGO_MCO.tex
add one bracket

\usepackage{hyperref}
\usepackage{cite}

@@

As noted earlier, the MCOlex problem at each stage (\ref{eq:9}) of the $\varepsilon$-constraint method is a global optimization problem with nonlinear constraints (\ref{eq:16}). Generally, the solution to such problems should start from the very beginning; and multiple solutions to such global optimization problems may require extensive calculations. However, the presence of search information $A_k$ from (\ref{eq:21}) allows bringing the results of previous calculations to the values of any next solved optimization problem in the scheme (\ref{eq:9}) without any time-consuming calculations of the values of the criteria $f_j (y)$, $1 \leq j \leq s$, of the problem (\ref{eq:1}) \cite{c30,c31}. 
{\color{red} 
This possibility of reusing search information can be briefly presented as follows.
\begin{itemize}
\item 
При минимизации очередного критерия $f_j(y(x)), 1\leq j\leq s,$ получаемая поисковая информация накапливается в форме множества $A_k$ из (\ref{eq:21}) (следует отметить, что в $A_k$ наряду со значениями $z_i, 1\leq i\leq k,$ минимизируемого критерия $f_j(y(x))$ запоминаются и вычисленные значения векторного критерия $f(y(x_i)), 1\leq i\leq k$.
\item 
При переходе к минимизации следующего критерия $f_{j+1}(y(x))$ значения этого критерия $z_i, 1\leq i\leq k,$ во всех точках $x_i, 1\leq i\leq k,$ ранее выполненных итераций глобального поиска могут получены при помощи быстро выполнимых вычислений на основе запомненных значений векторного критерия $f(y(x_i)), 1\leq i\leq k,$ в поисковой информации $A_k$
\begin{equation}\label{new_equation}
z'_i=Z(f(y(x_i))), 1\leq i\leq k,
\end{equation}
где процедура вычисления значений $z'_i, 1\leq i\leq k$ определяется правилами (\ref{eq:9}), (\ref{eq:18})--(\ref{eq:20}), без повторных вычислениях значений критериев $f_j(y(x)), 1\leq l\leq s$.
\end{itemize}
}
This reuse of search information to find the next efficient decision reduces the number of computations needed to solve each next optimization problem to just a few iterations -- see Section \ref{sec:5} for the results of numerical experiments.

>>>>

%\usepackage{hyperref}
\usepackage{cite}

@@

As noted earlier, the MCOlex problem at each stage (\ref{eq:9}) of the $\varepsilon$-constraint method is a global optimization problem with nonlinear constraints (\ref{eq:16}). Generally, the solution to such problems should start from the very beginning; and multiple solutions to such global optimization problems may require extensive calculations. However, the presence of search information $A_k$ from (\ref{eq:21}) allows bringing the results of previous calculations to the values of any next solved optimization problem in the scheme (\ref{eq:9}) without any time-consuming calculations of the values of the criteria $f_j (y)$, $1 \leq j \leq s$, of the problem (\ref{eq:1}) \cite{c30,c31}. 
{\color{red} This possibility of reusing search information can be briefly presented as follows.
\begin{itemize}
\item 
При минимизации очередного критерия $f_j(y(x)), 1\leq j\leq s,$ получаемая поисковая информация накапливается в форме множества $A_k$ из (\ref{eq:21}) (следует отметить, что в $A_k$ наряду со значениями $z_i, 1\leq i\leq k,$ минимизируемого критерия $f_j(y(x))$ запоминаются и вычисленные значения векторного критерия $f(y(x_i)), 1\leq i\leq k$).
\item 
При переходе к минимизации следующего критерия $f_{j+1}(y(x))$ значения этого критерия $z'_i, 1\leq i\leq k,$ во всех точках $x_i, 1\leq i\leq k,$ ранее выполненных итераций глобального поиска могут получены при помощи быстро выполнимых вычислений на основе запомненных значений векторного критерия $f(y(x_i)), 1\leq i\leq k,$ в поисковой информации $A_k$
\begin{equation}\label{new_equation}
z'_i=Z(f(y(x_i))), 1\leq i\leq k,
\end{equation}
где процедура вычисления значений $z'_i, 1\leq i\leq k$ определяется правилами (\ref{eq:9}), (\ref{eq:18})--(\ref{eq:20}), без повторных вычислениях значений критериев $f_j(y(x)), 1\leq l\leq s$.
\end{itemize}
}
This reuse of search information to find the next efficient decision reduces the number of computations needed to solve each next optimization problem to just a few iterations -- see Section \ref{sec:5} for the results of numerical experiments.
